---
title: "vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


## Installation

You can install the released version of iriR from [CRAN](https://CRAN.R-project.org) with:

``` r
devtools::install_github("warint/iriR")
```


## Installation

You can install the current development version of 'iriR' with:

```{r, eval = FALSE}
devtools::install_github("warint/spiR")
```


## How-To

### Step 1: Getting the country's ISO code

A user needs to enter the ISO code of a country. To have access to this code, the following function provides this information.

```{r, eval = FALSE}
sqs_iri_country() # A list of all countries will be produced

sqs_iri_country(country = "Canada") # The ISO code for Canada will be produced

sqs_iri_country("Canada") # The ISO code for Canada will be produced
```

### Step 2: Getting the indicator's code

A user needs to enter the code of the desired indicator. To do so, the following function provides access to all the indicators of interest.

```{r, eval = FALSE}
sqs_spi_indicator() # A list of all indicators will be produced

sqs_spi_indicator(indicators = "sales") # A list with all the variables including "sales" will be produced

sqs_spi_indicator("sales") # A list with all the variables including "sales" will be produced
```

### Step 3: Getting the company' name

A user needs to enter the name of the desired company. To do so, the following function provides access to all the companies of interest.

```{r, eval = FALSE}
sqs_iri_company() # A list of all companies will be produced

sqs_iri_company(company = "Samsung") # A list with all the variables including "Samsung" will be produced

sqs_spi_indicator("Samsung") # A list with all the variables including "Samsung" will be produced
```

### Step 4: Getting the industry' name

A user needs to enter the name of the desired industry. To do so, the following function provides access to all the industries of interest.


```{r, eval = FALSE}
sqs_iri_industry() # A list of all companies will be produced

sqs_iri_industry(industry = "Automobile") # A list with all the variables including "Automobile" will be produced

sqs_iri_industry("Automobile")# A list with all the variables including "Automobile" will be produced
```



### Step 5: Getting the data

Once the user knows all the arguments, s.he can collect the data in a very easy way through this function:

```{r, eval=FALSE}
sqs_iri_data(country = "USA", years = "2018", indicators = "RD.euro", company = "FORD MOTOR", industry = "Automobiles & Parts", rank = 14)  # It generates a data frame of the overall IRI data for American company "FORD MOTOR" in 2018.

sqs_iri_data(country=c("USA", "FRA"), years="2018",) # It generates a data frame of all the companies data from all the industries for the USA and France in 2018.

sqs_iri_data(years = "2018") # It generates a data frame of all the companies data for from all the industries for all the countries in 2018.

sqs_iri_data() # It generates a data frame of the complete dataset
```
